---
title: Mesocosm experiment plots
author: 
- |-
  _^1^ Department of Biology, Emory University, 1510 Clifton Road NE, Atlanta, GA, USA, 30322_
  _^2^ _
  ^['This Supplementary Material can be found at https://github.com/<_____>']
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
output:
  html_document:
    code_folding: hide
    depth: 3
    number_sections: no
    toc: yes
    toc_float: yes
  pdf_document:
    template: null
    toc: yes
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
inludes:
  before_body: before_body.tex
subtitle: Matthew Malishev^1^*
tags:
- nothing
- nothingness
abstract: "*Corresponding author: matthew.malishev@gmail.com  \n"
date: "`r Sys.Date()`"
classoption: landscape
vignette: >
  %\VignetteIndexEntry{Waddleometer test: Comparison of observed and predicted (waddleometer) body activity, body temperature and body mass}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r echo = FALSE}
# library(rmarkdown)
# setwd("/Users/malishev/Documents/Emory/research/models/deb/host_parasite/")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE  
)
```

## Overview

This document reads in the output produced by the file "Tiliqua rugosa simulation at Bundey Bore.Rmd" and the observed $T_b$, step count and body mass and compares them for each lizard in 2009 and 2010. It saves the summary statistics (correlation coefficient, root mean square error and confusion matrix) to files in the folder 'waddle test'. 

```{r, fig.width = 18, fig.height = 13, echo = FALSE, warning = FALSE, message = FALSE, include=TRUE} 
cat('\r\n\r\n')


# Loop through and plot

par(mfrow = c(2,2)) # set up for 5 plots in 2 columns
par(oma = c(2,2,2,2) + 0.1) # margin spacing stuff
par(mar = c(3,5,1,1) + 0.1) # margin spacing stuff 
par(mgp = c(3,1,0) ) # margin spacing stuff

############# start big loop to summarise all lizards, create Appendix 1 figs ######################
yearstodo=c(2009,2010)
for(m in 1:2){
  yeartodo=yearstodo[m]
  k=0
  # use individual 9 (burrows) or 115 (dam)
  for(i in 1:121){
    
    sleepy_id=waddlefiles[i,2]
    sexliz=subset(sex,Liz==sleepy_id)
    sexliz=sexliz[2]
    sexlizard=as.character(sexliz)
    if(sexlizard=="u" | sexlizard=="character(0)"){
      sexlizard='unknown'
    }
    if(sexlizard==2){
      sexlizard='F'
    }
    if(sexlizard==3){
      sexlizard='M'
    }
  }
}
    
```
```{r}

# loop through df's and plot 
# from Chapter4_figs.R
if(start.temp==start.temps[2]){
          par(new=T)
          axis(1,at=seq(0,days,by=length(temp$Tick)/4),labels=c("Sep","Oct","Nov","Dec",""))
          axis(2,at=0:2,labels=0:2,las=1)
          points(minTb,pch=20,
               ylim=c(0,2),
               type="p",
               col=ifelse(midday==1,col="purple", col <- colv),
               cex=minTb$y+0.5, 
               xlab="Days",ylab=paste0("Time to reach activity range temperature (hours)")
               )
          lines(lowess(minTb$x,minTb$y),col=colv)
          }else{
            plot(minTb,pch=20,
                 ylim=c(0,2),
                 type="p",
                 col=colv,
                 # cex=minTb$y+0.5,
                 cex=1,
                 xlab="Days",ylab=paste0("Time to reach activity range temperature (hours)"),
                 axes=F
                 )
            #abline(lm(minTb$y~minTb$x), col=colv) 
            lines(lowess(minTb$x,minTb$y),col=colv)
          }
        if(start.temp==start.temps[2]){dev.off()}
        }#end start.temps loop
    }
  }
```

