---
title: Mesocosm experiment plots
author: 
- |-
  _^1^ Department of Biology, Emory University, 1510 Clifton Road NE, Atlanta, GA, USA, 30322_
  ^['This Supplementary Material can be found at https://github.com/darwinanddavis/SchistoMesocosm']
#bibliography:/Users/malishev/Documents/Melbourne Uni/Thesis_2016/library.bib
output:
  html_document:
    code_folding: hide
    depth: 3
    number_sections: no
    toc: yes
    toc_float: yes
  pdf_document:
    template: null
    toc: yes
  word_document:
    highlight: tango
    keep_md: yes
    pandoc_args: --smart
    #reference: mystyles.docx
    toc: yes
includes:
  before_body: before_body.tex
subtitle: Matthew Malishev^1^*, David Civitello^1^
tags:
- nothing
- nothingness
params: 
  date: !r Sys.Date()
  version: !r getRversion()
  email: "matthew.malishev@gmail.com"
  dir: "/Users/malishev/Documents/Emory/research/mesocosm"
classoption: portrait
vignette: >
  %\VignetteIndexEntry{Mesocosm data for schisto shedding in snail hosts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<script type="text/x-mathjax-config">
  MathJax.Hub.Config({ TeX: { equationNumbers: {autoNumber: "all"} } });
</script>

```{r echo = FALSE}
# library(rmarkdown)
# setwd("/Users/malishev/Documents/Emory/research/models/deb/host_parasite/")
# f <- list.files()[1]
# render(f, output_format='pdf_document')
```

```{r, echo = FALSE}
knitr::opts_chunk$set(
 eval = TRUE, tidy.opts=list(width.cutoff=60), tidy=TRUE, echo=TRUE, warning = FALSE, message = FALSE
)
```

Date: `r params$date`  
R version: `r params$version`   
Corresponding author: `r params$email`

#### How much of the population does the sampling effort capture? 

## Overview  

This document uses the schisto mesocosm 2016 data to explore cercariae production from snail hosts of different body sizes (diameter in mm and mass in mg) over a 14 week period under high and low N/P nutrient conditions. Host reproduction (egg masses) is also calculated.    
  
---   
\   
  
### Install dependencies

```{r, load packages, include=F, cache=F, message=F}

packages <- c("rgdal","dplyr","zoo","RColorBrewer","viridis","plyr","digitize","jpeg","devtools","imager","dplyr","ggplot2","ggridges","ggjoy","ggthemes","svDialogs","data.table","tibble","extrafont","sp","gridExtra")   

if (require(packages)) {
  # install ggtech package from github for ggplot themes
  devtools::install_github("ricardo-bion/ggtech", 
                          dependencies=TRUE)

    install.packages(packages,dependencies = T)

    require(packages)

}

lapply(packages,library,character.only=T)
library(ggtech)
```


### Get data
```{r echo = TRUE, warning = FALSE, message = FALSE}
wd <- params$dir # working dir is set in yaml header
setwd(paste0(wd,"/"))
f <- "meso1.csv"
f2 <- "meso2.csv" 
```

### Load data
```{r}
meso1 <- read.table(f,header=T,sep=",", row.names=NULL,stringsAsFactors=FALSE, strip.white=TRUE) # read data
meso2 <- read.table(f2,header=T,sep=",",row.names=NULL,stringsAsFactors=FALSE, strip.white=TRUE) # read data
colnames(meso2)[2] <- "NP" # fix col names
meso2$Week <- as.integer(meso2$Week)
str(meso2)
meso1[is.na(meso1)] <- 0 ; meso2[is.na(meso2)] <- 0 # remove NAs
mass <- 0.0096*(meso1$Diameter^3) # add mass to df
meso1$Mass <- mass  
```

Outlier
```{r}
print("Outlier"); meso1[which(meso1$Mass==max(meso1$Mass)),]
outlier <- 0 # remove outlier from data?
if(outlier==1){meso1 <- subset(meso1,Mass<max(Mass))}
```

Cleaning Snail and Date cols
```{r}
#unique(meso1$Snail)
#unique(meso1$Date)
sapply(meso1, function(x) sum(nchar(x))) # check number of characters in each col
```

Set Cex sizes
```{r}
cex_cer <- (meso1$Cercariae+1)/1000
cex_sam <- meso1$Sampling_Effort/1.5
cex_diam <- meso1$Diameter/3
```

### Set plotting graphics  
```{r, cache = TRUE, tidy = TRUE, lazy = TRUE, results="hide"}
plot_it <- function(manuscript,bg,cp,alpha,family){ # plotting function (plot for MS or not, set bg color, set color palette from RColorBrewer, set alpha value for transperancy) 
  graphics.off()
  if(manuscript==0){
    if(bg=="black"){
      colvec<-magma(200,1)
      par(bg = colvec[1],col.axis="white",col.lab="white",col.main="white",fg="white",bty="n",las=1,mar=c(5,6,4,2),family=family) #mono
      border=adjustcolor("purple",alpha=0.5)
    }else{
      colvec<-bpy.colors(200)
      par(bg = colvec[1],col.axis="white",col.lab="white",col.main="white",fg="white",bty="n",las=1,mar=c(5,6,4,2),family=family) 
      border=adjustcolor("blue",alpha=0.5)
    }
  }else{
#    graphics.off()
    par(bty="n",las=1,family=family) 
  }
  # color palettes
  # ifelse(manuscript==1,colvec<-adjustcolor(brewer.pal(9,cp)[9], alpha = alpha),colvec <- adjustcolor(brewer.pal(9,cp)[5], alpha = alpha)) # fine tune plotting colors for plotting bg
   # colfunc <<- colorRampPalette(brewer.pal(9,cp),alpha=alpha)
  colfunc <<- adjustcolor(brewer.pal(9,cp),alpha=alpha) # USES <<- OPERATOR
}

# Setting ggplot theme graphics
plot_it_gg <- function(bg){ # bg = colour to plot bg, family = font family
  if(bg=="white"){
    bg <- "white"
    fg <- "black"
  theme_tufte(base_family = "HersheySans") +
    theme(panel.border = element_blank(),panel.grid.major = element_blank(),panel.grid.minor = element_blank(),panel.background = element_rect(fill = bg,colour = bg),plot.background = element_rect(fill=bg)) +
    theme(axis.line = element_line(color = fg)) +theme(axis.ticks = element_line(color = fg)) + theme(plot.title = element_text(colour = fg)) +theme(axis.title.x = element_text(colour = fg), axis.title.y = element_text(colour = fg)) + theme(axis.text.x = element_text(color = fg),axis.text.y = element_text(color = fg)) + theme(legend.key = element_rect(fill = bg)) + theme(legend.title = element_text(colour=fg)) + theme(legend.text = element_text(colour=fg))
}
  }# end gg
```

Set plotting parameters  

```{r, cache = TRUE, tidy = TRUE, lazy=TRUE, results="hide"}
print("1/0, set colour, set colour palette 'display.brewer.all()',set alpha for col,set font")
plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
plot_it_gg("white") # same as above

# set colors you want
col <- "lightblue" 
col2 <- "orange" 

```
  
Get only infected snails  
```{r}
# get only infected snails
meso1_II <- subset(meso1,subset=Cercariae>0)
meso1_UU <- subset(meso1,subset=Cercariae==0)
```

---
\  

##############################################################################
## Mesocosm1 data sheet

### Snail size per tank   
Shell diameter (mm) per tank    
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
par(mfrow=c(1,1))
ylim <- round_any(max(meso1$Diameter),10,ceiling)
boxplot(Diameter~Tank, data=meso1,
        ylim=c(0,ylim),
        col = "light blue",
        notch = T,xlab="Tank",ylab="Diameter (mm)",
        main=paste0("Shell diameter (mm) over ",max(meso1$Week)," weeks")
)
abline(h=mean(meso1$Diameter),col="pink",lty=3)
with(meso1,t.test(Diameter,Tank)) # t.test

```

### Snail diameter (mm) distribution
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
den <- density(meso1$Diameter)
xlim <- round_any(max(den$x),10,ceiling) 
ylim <- round_any(max(den$y),0.1,ceiling)
plot(den,
     col=adjustcolor(col,alpha=0.5),
     xlim=c(0,xlim),
     ylim=c(0,ylim),
     xlab="Diameter (mm)",
     ylab="Density",
     main=paste0("Overall shell diameter (mm) over ",max(meso1$Week)," weeks"))
polygon(den, col=adjustcolor(col,alpha=0.5),border=col) # fill AUC 
abline(v=mean(meso1$Diameter),col=col,lty=3,ylim=c(0,ylim)) # get mean
# un/infected diameter 
# Uninfected
den <- density(meso1_UU$Diameter)
plot(den,
     col=adjustcolor(col,alpha=0.5),
     xlim=c(0,xlim),
     ylim=c(0,ylim),
     xlab="Diameter (mm)",
     ylab="Density",
     main=paste0("Shell diameter (mm) over ",max(meso1$Week)," weeks"))
polygon(den, col=adjustcolor(col,alpha=0.5),border=col) # fill AUC 
abline(v=mean(meso1_UU$Diameter),col=col,lty=3,ylim=c(0,ylim)) # get mean
par(new=T)
# Infected 
den2 <- density(meso1_II$Diameter) 
plot(den2,
     col=adjustcolor(col2,alpha=0.5),
     xlim=c(0,xlim),
     ylim=c(0,ylim),
     xlab="",
     ylab="",
     main="")
polygon(den2, col=adjustcolor(col2,alpha=0.5),border=col2) # fill AUC 
abline(v=mean(meso1_II$Diameter),col=col2,lty=3,ylim=c(0,ylim)) # get mean
par(family="mono")
legend("right",legend=c("Uninfected","Infected"),col=c(col,col2),
       bty="n",pch=20,pt.cex=1.5,cex=0.7,y.intersp = 0.5, xjust = 0.5,
       title="",title.adj = 0.3,
       # text.font=2,
       trace=T,inset=0.1)
```

### Snail size over time (weeks)
Shell diameter (mm) over time (weeks)   
~1000 eggs inoculated at 0,2,4,6 weeks
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE)) # plot stacked plots
ylim <- round_any(max(meso1$Diameter),10,ceiling)
boxplot(Diameter~Week, data=meso1,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,ylim),
        col = col,
        notch = T,xlab="Week",ylab="Diameter (mm)",
        main=paste0("Shell diameter (mm) over ",max(meso1$Week)," weeks"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1$Diameter),col=col,lty=3)
par(new=T)
points(x=c(1,3,5,7),y=rep(ylim/2,4),pch="~",col="red")# add inoculation points
# un/infected
boxplot(Diameter~Week, data=meso1_UU,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,ylim),
        col = col,
        notch = T,xlab="Week",ylab="Diameter (mm)",
        main=paste0("Shell diameter (mm) over ",max(meso1$Week)," weeks \n(uninfected snails)"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1_UU$Diameter),col=col,lty=3)
par(new=T)
points(x=c(1,3,5,7),y=rep(ylim/2,4),pch="~",col="red")# add inoculation points

# infected
boxplot(Diameter~Week, data=meso1_II,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,ylim),
        col = col2,
        notch = T,xlab="Week",ylab="Diameter (mm)",
        main=paste0("Shell diameter (mm) over ",max(meso1$Week)," weeks \n (infected snails)"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1_II$Diameter),col=col,lty=3)
par(new=T)
points(x=c(1,3),y=rep(ylim/2,2),pch="~",col="red")# add inoculation points

```

### Snail size over time (weeks) per tank  

#### Snail size density over time for all tanks (total = 48) have been saved as 'Size_per_tank_over_time.pdf' in `r params$dir`  
\n
~1000 eggs inoculated at 0,2,4,6 weeks
```{r}

#### size dist per tank over time ('Snail size over time (weeks)' but for each tank)
# Plot Tanks with large nutrients at the beginning versus tanks with lower nutrients
# Pick high and low nutrient tanks to compare

# Focus on diameter rather than biomass

# Eight replicates per size class and NP combo: six received schisto, two didn't. (Replication factor)
```

```{r echo = T}
# Select tank #. Max 48   
tank <- 45
```

```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE)) # plot stacked plots
snail <- subset(meso1,subset=Tank==tank) # get tank level indiviudals

ggplot(snail, aes(x = Diameter, y = as.factor(Week), fill=..x..)) + # geom_density_ridges()
  # scale = overlap
  geom_density_ridges_gradient(scale = 5, size=0.2,color="black", rel_min_height = 0.01,panel_scaling=T,alpha=0.2) +
  geom_density_ridges(scale = 5, size=0.2,color="black", rel_min_height = 0.01,fill="white",alpha=0.2) +
  # geom_density_ridges(scale = 5, size=0.2,color="white", rel_min_height = 0.01,fill=col,alpha=0.5) +
  scale_fill_viridis(name = "Diameter", alpha=0.1, option = "magma",direction=-1) + # "magma", "inferno","plasma", "viridis", "cividis"
  xlim(c(0,25)) +
  labs(title = paste0("Snail diameter over ",max(meso1$Week)," weeks for tank ",tank)) +
  xlab("Snail diameter (mm)") +
  ylab("Week") +
  plot_it_gg("white")

```


```{r echo = F, results = "hide"}
# save plots for each tank to drive
tanks <- unique(meso1$Tank)

pdf("Size_per_tank_over_time.pdf",onefile = T)
# for (i in list(unique(meso1$Tank)[1:2])){
for(i in 1:length(tanks)){ 
par(bty="n", las = 1)
  snail <- subset(meso1,subset=Tank==i) # get tank level individuals
  grid.arrange( 
  ggplot(snail, aes(x = Diameter, y = as.factor(Week), fill=..x..)) + # geom_density_ridges()
    # scale = overlap
    geom_density_ridges_gradient(scale = 5, size=0.2,color="black", rel_min_height = 0.01,panel_scaling=T,alpha=0.2) +
    geom_density_ridges(scale = 5, size=0.2,color="black", rel_min_height = 0.01,fill="white",alpha=0.2) +
    # geom_density_ridges(scale = 5, size=0.2,color="white", rel_min_height = 0.01,fill=col,alpha=0.5) +
    scale_fill_viridis(name = "Diameter", alpha=0.1, option = "magma",direction=-1) + # "magma", "inferno","plasma", "viridis", "cividis"
    xlim(c(0,25)) +
    labs(title = paste0("Snail diameter over ", max(meso1$Week)," weeks for tank ",i)) +
    xlab("Snail diameter (mm)") +
    ylab("Week") +
    plot_it_gg("white")
  )
}  
dev.off()

```

### Body mass (mg) over time (weeks)   
(Soft tissue dry mass in mg = 0.0096 * Diameter[in mm]^3)   
~1000 eggs inoculated at 0,2,4,6 weeks   

Outer   
Outlier  
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))# plot stacked plots
ylim <- round_any(max(meso1$Mass),100,ceiling)
boxplot(Mass~Week, data=meso1,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,ylim),
        col = col,
        notch = T,xlab="Week",ylab="Dry body mass (mg)",
        main=paste0("Body mass (mg) over ",max(meso1$Week)," weeks"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1$Mass),col=col,lty=3)
points(x=c(1,3,5,7),y=rep(ylim/3,4),pch="~",col="red")# add inoculation points

### uninfected ###
boxplot(Mass~Week, data=meso1_UU,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,ylim),
        col = col,
        notch = T,xlab="Week",ylab="Dry body mass (mg)",
        main=paste0("Body mass (mg) over ",max(meso1$Week)," weeks \n(uninfected)"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1$Mass),col=col,lty=3)
points(x=c(1,3,5,7),y=rep(ylim/3,4),pch="~",col="red")# add inoculation points
### infected ###
ylim <- round_any(max(meso1_II$Mass),100,ceiling)
boxplot(Mass~Week, data=meso1_II,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,ylim),
        col = col2,
        notch = F,xlab="Week",ylab="Dry body mass (mg)",
        main=paste0("Body mass (mg) over ",max(meso1$Week)," weeks \n(infected)"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1$Mass),col=col2,lty=3)
points(x=c(1,3),y=rep(ylim/1.2,2),pch="~",col="red")# add inoculation points
```


**Without outlier**    

Outlier  

```{r}
outer <- meso1[which(meso1$Mass==max(meso1$Mass)),][,c("Mass","Cercariae")] # identify outlier
outer
```


```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))# plot stacked plots
ylim <- round_any(max(meso1$Mass),100,ceiling)
boxplot(Mass~Week, data=meso1,
        outline = F,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,60),
        col = col,
        notch = T,xlab="Week",ylab="Dry body mass (mg)",
        main=paste0("Body mass (mg) over ",max(meso1$Week)," weeks without outlier"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1$Mass),col=col,lty=3)
points(x=c(1,3,5,7),y=rep(ylim/3,4),pch="~",col="red")# add inoculation points

### uninfected ###
boxplot(Mass~Week, data=meso1_UU,outline=F,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,60),
        col = col,
        notch = T,xlab="Week",ylab="Dry body mass (mg)",
        main=paste0("Body mass (mg) over ",max(meso1$Week)," weeks  \n(uninfected)"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1$Mass),col=col,lty=3)
points(x=c(1,3,5,7),y=rep(ylim/3,4),pch="~",col="red")# add inoculation points
### infected ###
ylim <- round_any(max(meso1_II$Mass),100,ceiling)
boxplot(Mass~Week, data=meso1_II,
        # xlim=c(0,max(meso1$Week)),
        ylim=c(0,ylim),
        col = col2,
        notch = F,xlab="Week",ylab="Dry body mass (mg)",
        main=paste0("Body mass (mg) over ",max(meso1$Week)," weeks  \n(infected)"),
        xaxs = "i", yaxs = "i"
)
abline(h=mean(meso1$Mass),col=col2,lty=3)
points(x=c(1,3),y=rep(ylim/1.2,2),pch="~",col="red")# add inoculation points
```

### Snail size and number of cercariae produced  
Point size by cercariae number  
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
with(meso1,plot(Diameter,log(Cercariae),pch=20,
                col=adjustcolor(col,alpha=0.5),
                cex=cex_cer+0.5,
                ylab="Log number of cercariae released over 90 mins",xlab=" Diameter (mm)"
))
title("Number of cercarie for each snail length (mm)")
abline(v=mean(meso1$Diameter),lty=3,col=col)# mean diameter
points(outer,col="red",pch=20) # plot outlier
```
Linear log
```{r}
# summary(with(meso1,lm(log(Cercariae)~Diameter))) # linear log
```

### Snail mass and cercariae produced (mg)
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
with(meso1,plot(log(Mass),Cercariae,pch=20,
                col=adjustcolor(col,alpha=0.5),
                cex=cex_cer+0.5,
                # cex=1.5,
                ylab="Number of cercariae released over 90 mins",xlab="Log dry body mass (mg)"))
title("Number of cercariae for each log snail mass (mg)")
abline(v=log(mean(meso1$Mass)),lty=3,col=col)# mean diameter
outer <- meso1[which(meso1$Mass==max(meso1$Mass)),][,c("Mass","Cercariae")] # identify outlier
points(outer,col="red",pch=20) # plot outlier
```

### Snail size per tank   
Shell diameter (mm)   
Select tank #. max 48   
```{r}
tank <- 2
```

```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE)) # plot stacked plots
snail <- subset(meso1,subset=Tank==tank) # get tank level indiviudals
diam_total <- 1 # set ylim either to max for tank or max across all tanks (16.8)
den <- density(snail$Diameter) # get diameter density
xlim <- round_any(max(den$x),10,ceiling)
ylim <- round_any(max(den$y),0.05,ceiling)
plot(den,
     col=adjustcolor(col,alpha=0.5),
     xlim=c(0,xlim),ylim=c(0,ylim),
     xlab="",ylab="",main=""
)
polygon(den, col=adjustcolor(col,alpha=0.5),border=col) # fill AUC
abline(v=mean(snail$Diameter),col=col,lty=3,ylim=c(0,ylim)) # get mean
title(main=paste0("Shell diameter (mm) distribution for tank #",tank),
      xlab="Shell diameter (mm)")
title(ylab="Density",line=3.5)

### uninfected ###
snail_UU <- subset(snail,subset=Cercariae==0)
den <- density(snail_UU$Diameter) # get diameter density
xlim <- round_any(max(den$x),10,ceiling)
ylim <- round_any(max(den$y),0.05,ceiling)
plot(den,
     col=adjustcolor(col,alpha=0.5),
     xlim=c(0,xlim),ylim=c(0,ylim),
     xlab="",ylab="",main=""
)
polygon(den, col=adjustcolor(col,alpha=0.5),border=col) # fill AUC
abline(v=mean(snail_UU$Diameter),col=col,lty=3,ylim=c(0,ylim)) # get mean
title(main=paste0("Uninfected snails in tank #",tank),
      xlab="Shell diameter (mm)")
title(ylab="Density",line=3.5)

### infected ###
snail_II <- subset(snail,subset=Cercariae>0)
if(length(snail_II$Tank)>0){
  den2 <- density(snail_II$Diameter) # get diameter density
  plot(den2,
       col=adjustcolor(col2,alpha=0.5),
       xlim=c(0,xlim),ylim=c(0,ylim),
       xlab="",ylab="",main=""
  )
  polygon(den2, col=adjustcolor(col2,alpha=0.5),border=col2) # fill AUC
  abline(v=mean(snail_II$Diameter),col=col2,lty=3,ylim=c(0,ylim)) # get mean
  title(main=paste0("Infected snails in tank #",tank),
        xlab="Shell diameter (mm)")
}else{
  plot(0,0,type="n");title(main=paste0("Infected snails in tank #",tank)); text(0,0.5,paste0("No cercariae \nin tank #",tank))
}

```

### Cercariae production over time    
Cercariae shed over 90 mins per week    
~1000 eggs inoculated at 0,2,4,6 weeks    
Snail abundance over time (weeks)    
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
xlim <- max(meso1$Week) # uses total num of weeks
ylim <- round_any(max(meso1$Cercariae),100,ceiling)
with(meso1,plot(Cercariae~Week,
                col=adjustcolor(col,alpha=0.5),
                type="h",
                lwd=5,
                xlim=c(0,xlim),ylim=c(0,ylim),
                xlab="",ylab="",main=""
))
abline(h=mean(meso1$Cercariae),col=col,lty=3,ylim=c(0,ylim)) # get mean
title(main=paste0("Cercariae production over ",max(meso1$Week)," weeks"),
      xlab="Week")
title(ylab="Number of cercariae shed in 90 mins",line=3.5)
```


### Tank cercariae production over time per tank  

Select tank #. max 48
```{r}
tank <- 9
```

```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
cer_total <- 0 # set ylim either to max for tank (1) or max across all tanks (6100)

snail <- subset(meso1,subset=Tank==tank) # get tank level individuals
snail <- subset(snail,subset=Cercariae>0) # get only cercariae
xlim <- max(meso1$Week) # uses total num of weeks
ylim <- round_any(max(snail$Cercariae),100,ceiling)
ifelse(cer_total==1,ylim <- round_any(max(meso1$Cercariae),100,ceiling),ylim <- round_any(max(snail$Cercariae),100,ceiling))
par(mfrow=c(1,1))
if(length(snail$Cercariae)>0){
  with(snail,plot(Cercariae~Week,
                  col=adjustcolor(col,alpha=0.5),
                  type="h",
                  lwd=5,
                  xlim=c(0,xlim),ylim=c(0,ylim),
                  xlab="",ylab="",main=""
  ))
  abline(h=mean(snail$Cercariae),col=col,lty=3,ylim=c(0,ylim)) # get mean
  title(main=paste0("Cercariae production for tank ",tank," over ",max(meso1$Week)," weeks"),
        xlab="Week")
  title(ylab="Number of cercariae shed in 90 mins",line=3.5)
  par(new=T)
  points(x=c(0,2,4,6),y=rep(max(snail$Cercariae)/3,4),pch="~",cex=1.5,col="red")# add inoculation points
}else{print(paste0("No cercariae in tank #",tank))}

#####

############################################################################################################
############################################################################################################
############################################################################################################

```

#####
## Mesocosm 2 data sheet
Clean data
```{r}
meso2$Schisto <- as.integer(as.factor(meso2$Schisto))-1# convert Y/N in Schisto col to 1/0
# convert size to integers
meso2$Size <- gsub("Intermediate","2Intermediate",meso2$Size)
meso2$Size <- gsub("Small","1Small",meso2$Size)
meso2$Size <- gsub("Large","3Large",meso2$Size)
meso2$Size <- as.integer(as.factor(meso2$Size))

### get snails with egg masses
#### First get presence of schisto
meso2_UU <-  subset(meso2,Schisto==0)
meso2_II <- subset(meso2,Schisto==1)

# get uninfected snails with egg masses
eggs_UU <- subset(meso2_UU,Eggs>0)
# get infected snails with egg masses
eggs_II <- subset(meso2_II,Eggs>0)

# get size classes
small <- subset(meso2,Size==1) #small
int <- subset(meso2,Size==2) #intermediate
large <- subset(meso2,Size==3) #large

# get NP conc
high <- subset(meso2,NP=="High") # high NP conc
low <- subset(meso2,NP=="Low") # low NP conc
```
### Egg mass distribution


```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
den <- density(meso2$Eggs[meso2$Eggs>0]) # get only snails with eggs
xlim <- round_any(max(den$x),50,ceiling)
ylim <- round_any(max(den$y),0.01,ceiling)
plot(den,
     col=adjustcolor(col,alpha=0.5),
     xlim=c(0,xlim),
     ylim=c(0,ylim),
     xlab="Number of egg masses",
     ylab="Density",
     main=paste0("Distribution of number of egg masses over ",max(meso1$Week)," weeks"))
polygon(den, col=adjustcolor(col,alpha=0.5),border=col) # fill AUC
abline(v=mean(meso2$Eggs),col=col,lty=3,ylim=c(0,ylim)) # get mean
```

### N/P concentration v egg mass   

```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE)) # plot stacked plots
ylim=round_any(max(meso2$Eggs),10)
with(meso2,stripchart(Eggs~NP,
                      method="jitter", jitter=0.1,
                      pch=20,cex=2,
                      # cex=cex_diam,
                      col=adjustcolor(col,alpha=0.3),
                      vertical=T,
                      ylim=c(0,ylim),
                      group.names=c("High","Low"),
                      xlab="",ylab="",main="")
)
abline(h=mean(meso2$Eggs),col=col,lty=3)
title(main=paste0("Number of egg masses for high and low N/P levels over ",max(meso1$Week)," weeks"),
      xlab="N/P level")
title(ylab="Number of egg masses",line=3.5)

### uninfected ###
with(eggs_UU,stripchart(Eggs~NP,
                        method="jitter", jitter=0.1,
                        pch=20,cex=2,
                        col=adjustcolor(col,alpha=0.3),
                        vertical=T,
                        ylim=c(0,ylim),
                        group.names=c("High","Low"),
                        xlab="",ylab="",main="")
)
abline(h=mean(eggs_UU$Eggs),col=col,lty=3)
title(main=paste0("Uninfected snails"),
      xlab="N/P level")
title(ylab="Number of egg masses",line=3.5)

### infected ###
with(eggs_II,stripchart(Eggs~NP,
                        method="jitter", jitter=0.1,
                        pch=20,cex=2,
                        col=adjustcolor(col2,alpha=0.3),
                        vertical=T,
                        ylim=c(0,ylim),
                        group.names=c("High","Low"),
                        xlab="",ylab="",main="")
)
abline(h=mean(eggs_II$Eggs),col=col2,lty=3)
title(main=paste0("Infected snails"),
      xlab="N/P level")

```

### Phyto and Peri Distribution    

phyto = flourescence units    
peri = flourescence per 2 weeks / 3.5 inch^2 tile (gross productivity biomass rate)    

```{r}
par(bty="n", las = 1)
par(mfrow=c(1,1))
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
den <- density(meso2$Phyto_F)
xlim <- round_any(max(den$x),10000,ceiling)
ylim <- round_any(max(den$y),0.0001,ceiling)
plot(den,
     col=adjustcolor(col,alpha=0.5),
     xlim=c(0,xlim),
     ylim=c(0,ylim),
     xlab="",ylab="",main=""
)
polygon(den, col=adjustcolor(col,alpha=0.5),border=col) # fill AUC
abline(v=mean(meso2$Phyto_F),col=col,lty=3,ylim=c(0,ylim)) # get mean
par(new=T) # add periphyton concentration
den2 <- density(meso2$Peri_F)
plot(den2,
     col=adjustcolor(col2,alpha=0.5),
     xlim=c(0,xlim), # uses xy lims from phyto
     ylim=c(0,ylim),
     xlab="",ylab="",main=""
)
polygon(den2, col=adjustcolor(col2,alpha=0.5),border=col2) # fill AUC
abline(v=mean(meso2$Peri_F),col=col2,lty=3,ylim=c(0,ylim)) # get mean
title(main=paste0("Resource concentration over ",max(meso1$Week)," weeks"),
      xlab="Resource concentration")
title(ylab="Density",line=3.5)
par(family='mono')
legend("topright",legend=c("Phytoplankton","Periphyton"),title="Resource type",
       border="white",pch=19,ncol=1,bty="n",
       cex=0.75,
       xjust=0.5,yjust=0.5,x.intersp = 0.5,y.intersp = 0.5,
       col=c(col,col2)
)
```

### Egg Mass over time v presence of schisto
~1000 eggs inoculated at 0,2,4,6 weeks
```{r}
par(bty="n", las = 1)
#plot_it(0,"blue","YlOrRd",1,"HersheySans") # set col function params
layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE)) # plot stacked plots
par(mar=c(3.5,5,2,2))
meso2$Week <- as.integer(meso2$Week)
xlim <- max(meso2$Week)
ylim <- round_any(max(meso2$Eggs),10)
with(meso2,stripchart(Eggs~Week,
                      method="jitter", jitter=0.1,
                      pch=20,cex=2,
                      col=adjustcolor(col,alpha=0.5),
                      vertical=T,
                      xlim=c(0,xlim), ylim=c(0,ylim),
                      group.names=unique(meso2$Week),
                      xlab="Weeks",
                      ylab="Number of egg masses",
                      main=paste0("Number of egg masses over ",xlim," weeks")
))
abline(h=mean(meso2$Eggs),col=col,lty=3)
par(new=T)
points(x=c(0,2,4,6),y=rep(max(ylim)/3,4),pch="~",cex=1,col="red")# add inoculation points
axis(1,at=c(0,xlim),labels=c("0",""))# bookending axis tick marks

### uninfected ###
with(eggs_UU, stripchart(Eggs~Week,
                         method="jitter", jitter=0.1,
                         pch=20,cex=2,
                         col=adjustcolor(col,alpha=0.3),
                         vertical=T,
                         xlim=c(0,xlim),ylim=c(0,ylim),
                         group.names=unique(eggs_UU$Week),
                         xlab="Weeks",
                         ylab="Number of egg masses",
                         main="Uninfected")
)
par(new=T)
points(x=c(0,2,4,6),y=rep(max(ylim)/3,4),pch="~",cex=1,col="red")# add inoculation points
axis(1,at=c(0,xlim),labels=c("0","16"))# bookending axis tick marks

### infected ###
with(eggs_II, stripchart(Eggs~Week,
                         method="jitter", jitter=0.1,
                         pch=20,cex=2,
                         col=adjustcolor(col2,alpha=0.3),
                         vertical=T,
                         xlim=c(0,xlim),ylim=c(0,ylim),
                         group.names=unique(eggs_II$Week),
                         xlab="Weeks",
                         ylab="Number of egg masses",
                         main="Infected")
)
par(new=T)
points(x=c(0,2,4,6),y=rep(max(ylim)/3,4),pch="~",cex=1,col="red")# add inoculation points
axis(1,at=c(0,xlim),labels=c("0","16"))# bookending axis tick marks
### Size class vs peri
#~1000 eggs inoculated at 0,2,4,6 weeks

```

### Size class vs Egg mass (with schisto)


```{r}
par(bty="n", las = 1)
#### Egg masses > 0
den <- density(small$Eggs[small$Eggs>0])
den2 <- density(int$Eggs[int$Eggs>0])
den3 <- density(large$Eggs[large$Eggs>0])
xlim <- round_any(max(den2$x),100) #den2 xlim
ylim <- round_any(max(den2$y),0.01,ceiling) # den2 ylim

colvec <- c(4,6,9) # index for colfunc color palette in plot_it function
par(mfrow=c(1,1))
plot(den,
     col=adjustcolor(colfunc[colvec[1]],alpha=0.5),
     xlim=c(0,xlim),
     ylim=c(0,ylim),
     # type="h",# fills density
     xlab="Number of egg masses",
     ylab="Density",
     main="Number of egg masses for each snail size class"
)
lines(den2,col=adjustcolor(colfunc[colvec[2]])) # den2
lines(den3,col=adjustcolor(colfunc[colvec[3]])) # den3
# fill densities
polygon(den, col=adjustcolor(colfunc[colvec[1]],alpha=0.5),border=colfunc[colvec[1]]) # fill AUC
polygon(den2, col=adjustcolor(colfunc[colvec[2]],alpha=0.5),border=colfunc[colvec[2]]) # fill AUC
polygon(den3, col=adjustcolor(colfunc[colvec[3]],alpha=0.5),border=colfunc[colvec[3]]) # fill AUC
# means
abline(v=mean(small$Eggs),col=adjustcolor(colfunc[colvec[1]]),lty=3,ylim=c(0,ylim)) # get mean
abline(v=mean(int$Eggs),col=adjustcolor(colfunc[colvec[2]]),lty=3,ylim=c(0,ylim)) # get mean
abline(v=mean(large$Eggs),col=adjustcolor(colfunc[colvec[3]]),lty=3,ylim=c(0,ylim)) # get mean

par(family="mono")
legend("right",legend=c("Small","Intermediate","Large"),col=c(colfunc[colvec[1:3]]),
       bty="n",pch=20,pt.cex=1.5,cex=0.7,y.intersp = 0.5, xjust = 0.5,
       title="Snail size class",title.adj = 0.3,text.font=2,
       trace=T,inset=0.1)

### Uninfected
small_UU <- subset(small,Schisto==0)
int_UU <- subset(int,Schisto==0)
large_UU <- subset(large,Schisto==0)
### Infected
small_II <- subset(small,Schisto==1)
int_II <- subset(int,Schisto==1)
large_II <- subset(large,Schisto==1)

```

### Egg Mass per Week


~1000 eggs inoculated at 0,2,4,6 weeks


```{r}
par(bty="n", las = 1)
# set data to appropriate class
meso2$Eggs <- as.numeric(meso2$Eggs)
d <- meso2
ggplot(meso2, aes(x = Eggs, y = as.factor(Week), fill=..x..)) + # geom_density_ridges()
  # geom_density_ridges_gradient(scale = 2, size=0.25, rel_min_height = 0.01,panel_scaling=T) +# scale = overlap
  # scale_fill_viridis(name = "Eggs", alpha=0.5, option = "magma",direction=-1) + # "magma", "inferno","plasma", "viridis", "cividis"
  geom_density_ridges(scale = 3, size=0.2,color="black", rel_min_height = 0.01,fill=col,alpha=0.5) +
  labs(title = paste0("Number of egg masses per week ")) +
  xlab("Number of egg masses") +
  ylab("Week") +
  # theme_ridges(grid=F,center_axis_labels = T)
  plot_it_gg("white")

#### uninfected ####
par(bty="n", las = 1)
ggplot(meso2_UU, aes(x = Eggs, y = as.factor(Week), fill=..x..)) + # geom_density_ridges()
  # geom_density_ridges_gradient(scale = 2, size=0.25, rel_min_height = 0.01,panel_scaling=T) +# scale = overlap
  # scale_fill_viridis(name = "Eggs", alpha=0.5, option = "magma",direction=-1) + # "magma", "inferno","plasma", "viridis", "cividis"
  geom_density_ridges(scale = 3, size=0.2,color="black", rel_min_height = 0.01,fill=col,alpha=0.5) +
  labs(title = paste0("Number of egg masses per week for uninfected hosts")) +
  xlab("Number of egg masses") +
  ylab("Week") +
  # theme_ridges(grid=F,center_axis_labels = T)
  plot_it_gg("white")

#### infected ####
par(bty="n", las = 1)
ggplot(meso2_II, aes(x = Eggs, y = as.factor(Week), fill=..x..)) + # geom_density_ridges()
  # geom_density_ridges_gradient(scale = 2, size=0.25, rel_min_height = 0.01,panel_scaling=T) +# scale = overlap
  # scale_fill_viridis(name = "Eggs", alpha=0.5, option = "magma",direction=-1) + # "magma", "inferno","plasma", "viridis", "cividis"
  geom_density_ridges(scale = 3, size=0.2,color="black", rel_min_height = 0.01,fill=col2,alpha=0.5) +
  labs(title = paste0("Number of egg masses per week for infected hosts")) +
  xlab("Number of egg masses") +
  ylab("Week") +
  # theme_ridges(grid=F,center_axis_labels = T)
  plot_it_gg("white")

```




